Layered Formal Verification of an Industrial TCP/IP Stack

### 2021-05-21 SecDev21/paper.tex
interfacing data objects text fixes

@@

Hopefully, SPARK integrates a mechanism to interface C code. No verification are
performed on the C code, but pre- and postconditions can be attached to
subprograms and they can be called in SPARK code.
The functional specification are not proved, thus it is the role of the
programmer to ensure the correctness of the contracts.

The types in SPARK can be more expressive than the types in C which adds more
safety to the SPARK code.
But the C and the SPARK code can share objects and it is essential that the
memory representations of an object are the same in the C and in the SPARK side.
For instance, if a C function is supposed to be called with a 32-bits integer,
it is the responsibility of the programmer to ensure that the function is
actually called with a 32-bits integer in the SPARK code.

>>>>

Ada and SPARK offer an easy-to-use mechanism for interfacing with C code \cite{}. The mechanism allows C-written function to be called by Ada/SPARK code and vice versa and for representing shared data objects. The memory representations of a shared data object must be the same in both the C and the SPARK code. For instance, if a C function is called with a 32-bits integer argument, the SPARK interface of this function should also be called with a 32-bits integer argument. It is the responsibility of the user to ensure this.

@@

No verification are
performed on the C code, but pre- and postconditions can be attached to
subprograms and they can be called in SPARK code.
The functional specification are not proved, thus it is the role of the
programmer to ensure the correctness of the contracts.
